\chapter*{Dedications}
\hspace{1cm} I am pleased to dedicate this page of my internship report to express my deep appreciation and sincere gratitude to all the people who believed in me and kept supporting me throughout my academic career.\bigskip

\textbf{My parents:} It is with infinite gratitude that I dedicate this work to my dear parents, who have always been a source of motivation and inspiration for my studies. Their advice and unconditional support have been invaluable.
I am particularly grateful to my mother, who has been by my side to encourage me and who has made countless sacrifices for my happiness. My father, a precious blessing, has always had confidence in me, from the first day of school.\bigskip

\textbf{My sisters:} I would also like to dedicate this work to my sisters, who have always been encouraging and supportive to me. Their contribution to my personal development has been invaluable, and has helped me cross a horizon in my life. I wish them even more success in their paths.\bigskip

\textbf{To all my loved ones,} what I have become today, I owe it to your unconditional love, your patience and your many sacrifices.
May this work be a modest way of expressing my gratitude to you, for all that you have done in my favor.\bigskip

\textbf{May God, the Almighty,} grant you good health and a long life, so that I can in turn fill you with well-being. My love for you is deep and sincere.

\chapter*{Acknowledgements}
\hspace{1cm} At the end of this work, I would like to express my sincere gratitude, accompanied by all my respect, to those who have helped me throughout the realization of this present project.\bigskip

First of all, I thank the Almighty God for granting me the prosperity, courage and energy necessary to take up the challenge and successfully carry out the realization of this project.\bigskip

I would like to express my gratitude to my academic supervisor, \textbf{Mrs. Chifaa GHANMI}, for her understanding and availability. She is, truly, a major pillar of this achievement. Her support played a crucial role in the success of this project.\bigskip

I would also like to express my sincere gratitude to my professional supervisor, \textbf{Mr. Hazem RAOUAFI}, who is also a pillar of this success, for his assistance and advice throughout this internship period.\bigskip

I would also like to thank the entire team of the company, \textbf{Standard Sharing Software}, for their hospitality and inclusiveness.\bigskip

Finally, I would like to express my gratitude to \textbf{the members of the jury} for having valued my work and for their precious attention.\bigskip

I would like to conclude by expressing my gratitude and my greatest respect to \textbf{all the professors and staff at ESPRIT}. It is thanks to their efforts and the exceptional quality of the teaching provided within the school that I was able to benefit from an up-to-date training which played a relevant role in the achievement of my success.